Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
using the same style.
Wording of Problem -> Doctest and Haddock

A good candidate to describe evidence for users is Doctest in Python community.
It extends Python's documentation strings so that they
can contain examples.
Examples can be tested by the Python interpreter.

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock defines markup syntax in Haskell's comment.
Haddock provides markup for code blocks, indicated with ({\tt >}).
For example, the {\tt containers} packages has the following code block markup:

>>>>

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock provides markup syntax for code blocks, indicated with ({\tt
>}).
For example, the {\tt containers} packages contains a Haddock comment
with the following code block.
